Reproduce anaylses of Beninca et al (2008)

### 2016-02-23 code/report.Rmd
report updated with latest r-squared

<!--
Until the close HTML comment are some code Owen was previously using to calculate the predictability decline.

Need to predict until about 40 days ahead = 40 / 3.35 time steps = 12 time steps. Do this from each time in the time series as initial abundances.

From each time in the series, predict 12 steps ahead. Put results in an array: time x species x start.location.
time will be 12, species will be 12, start location will be length of time series - 12

```{r}
## some preliminaries
x <- X 
Z <- LE[[3]]
Z1 <- Z[,13:24]
all.species <- names(all.gams)
time.to.predict <- 12
nn <- length(Z1[,1])-time.to.predict
## create the array of predictions
preds <- array(NA, c(12, 12, nn))
dimnames(preds) <- list(dist=1:12,
                        species=all.species,
                        start.time=1:nn)
## fill in the array with the one step ahead predictions
for(i in 1:length(all.species))
  preds[1,i,] <- predict(all.gams[[i]])[1:nn]

# Now for the predictions at t+2 from predictions at t+1
pred.time <- 2
for(pred.time in 2:12) {
  for(i in 1:length(all.species))
    preds[pred.time,i,pred.time:nn] <- predict(all.gams[[i]],
                                                newdata=as.data.frame(t(preds[pred.time-1,,])))[pred.time:nn]
}
```

Get the correlations and do some house keeping:
```{r}
cors <- matrix(NA, 12, 12)
dimnames(cors) = list(dist=1:12,
                        species=names(x))
for(i in 1:12) {
  for(j in 1:12) {
    cors[j,i] <- cor(Z1[1:nn,i], preds[j, i, ], use="complete.obs")^2
}}
cors <- data.frame(dist=as.numeric(I(rownames(cors))), cors)
cors.long <- gather(as.data.frame(cors), key=dist)
names(cors.long) <- c("Prediction_distance", "Variable", "Correlation")
```

@@

ggplot(cors.long, aes(x=Prediction_distance*3.75, y=Correlation)) +
  xlab("Prediction time (days)") +
  geom_point(col="red") +
  facet_wrap(~Variable, ncol=3 ) +
  geom_point(data=filter(opw, Model=="nonlinear"),
             aes(x=prediction_time, y=r_squared))

>>>>

@@

ggplot(filter(cors.long, Prediction_distance<13),
       aes(x=Prediction_distance*3.35, y=Correlation)) +
  xlab("Prediction time (days)") +
  geom_point(col="red") +
  facet_wrap(~Variable, ncol=3 ) +
  geom_point(data=filter(opw, Model=="nonlinear"),
             aes(x=prediction_time, y=r_squared)) +
  ylim(0,1)
